\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[margin=1in]{geometry}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage{array}

\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=2em}
\setlength{\columnsep}{0.5cm}

\hypersetup{colorlinks=true, urlcolor=black}

\begin{document}

\vspace*{-6.5em}
\begin{center}
    \href{https://menasy.me/}{\LARGE \textbf{Mehmet Nasim Yılmaz}}
\end{center}
\vspace*{0.5em}
\noindent
\begin{minipage}[t]{0.48\textwidth}
    \begin{tabular}{@{}l}
        \textbf{LinkedIn:} \href{https://linkedin.com/in/menasy}{linkedin.com/in/menasy} \\
        \textbf{GitHub:} \href{https://github.com/menasy}{github.com/menasy} \\
        \textbf{Portfolio:} \href{https://menasy.me/}{menasy.me} \\
    \end{tabular}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.48\textwidth}
    \raggedleft
    \begin{tabular}{@{}l}
        \textbf{Location:} Istanbul \\
        \textbf{Date of Birth:} 02.02.2000 \\
        \textbf{E-mail:} mehmetnasim42@gmail.com \\
    \end{tabular}
\end{minipage}

\vspace{0.5em}

% Summary
I focus on software development, web technologies, and mobile programming. \textit{"There is nothing I do not know, only things I have not yet learned."} With this mindset, I keep improving myself. I believe I have built a solid foundation with the technical knowledge and experience I have gained so far. My goal is to create innovative projects, add value to the teams I join, and do meaningful work in the industry.
\vspace{-0.2em}

You can visit my \textbf{\href{https://medium.com/@menasy}{Medium}} for blog posts, and my \textbf{\href{https://menasy.me/}{portfolio}} for all my projects and detailed information. Working at your company would be a great opportunity for me. Thank you for your interest.

\vspace{-0.1em}

\textbf{Education}
\vspace{-0.5em}
\begin{itemize}
  \item Istanbul Gelisim University – Management Information Systems / 2021 - 2025
\end{itemize}

\vspace{-0.4em}

\textbf{Experience}
\vspace{-0.5em}
\begin{itemize}

  \item \textbf{42 Istanbul – Software Engineer / 09.10.2023 - 15.01.2026}
    
    I worked on various software projects, from C/C++, multithreading, sockets, and microservices to full-stack web development with TypeScript.
  \item \textbf{Baykar Technology – Central Control Software Intern / 06.10.2025 - 27.12.2025}
  
    I developed a full-stack live streaming platform using Wowza, .NET, and React.
  
  \item \textbf{Paka Technology – System Support Intern / 12.08.2024 – 23.09.2024}
  
  I worked on IT infrastructure management and hardware/software support operations.
  
  \item \textbf{Tencent Holdings Limited – Server Technician / 01.04.2023 – 01.05.2023}
  
We completed server installation, rack placement, and cabling as a team.
\end{itemize}

\vspace{-0.4em}

\textbf{Featured Projects}
\vspace{-0.5em}
\begin{itemize}
    \item \textbf{eSIMeco - Web:} A production-ready eSIM purchase platform built with Next.js.
    \item \textbf{Ft-transcendence - Web Game:} We rebuilt the classic Pong game as a team of four with modern web technologies.
    \item \textbf{Webserv - Web Server:} My teammate and I built a web server from scratch with C++ and socket programming, supporting HTTP/1.1 and NGINX-like behavior.
  \item \textbf{Inception - Microservice:} I built a web-based microservice architecture with Docker.
    \item \textbf{HesKit - Mobile:} I developed an employee management application using Java/SQL.
    \item \textbf{Central Health App - Mobile:} Kotlin, Firebase based appointment/prescription system.
  \item \textbf{Smart Guide - Mobile:} I developed and published an accessibility-focused contact application on the Play Store using React Native.
\end{itemize}

\vspace{-0.5em}

% İlk satır: Programlama Dilleri & Programlama Becerileri
\noindent
\begin{minipage}[t]{0.48\textwidth}
    \textbf{Programming Languages}
    \vspace{0em}
    \begin{itemize}
        \item C (expert)
        \item Git/GitHub(expert)
        \item C\#/ASP.NET (advanced)
        \item JavaScript/TypeScript (advanced)
        \item React/Next.js/React Native (advanced)
        \item C++ (intermediate)
        \item Java (intermediate)
        \item Kotlin (intermediate)
        \item SQL/PostgreSQL (intermediate)
        \item HTML/Tailwind/CSS (intermediate)
        \item XML (intermediate)
        \item Python (basic)
    \end{itemize}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.48\textwidth}
    \textbf{Programming Skills}
    \vspace{0em}
\begin{itemize}
\item Object-Oriented Programming
        \item Multi Process and Multi Thread
        \item Docker/Microservice Architecture
        \item Monitoring and Log Management
        \item Component-Based Architecture
        \item Onion and MVC Architecture 
        \item Asynchronous Programming 
        \item Full-Stack Development
        \item Server Side Rendering
        \item REST API
        \item CI/CD
        \item Linux
\end{itemize}
\end{minipage}

\vspace{0.1em}
\noindent
\begin{minipage}[t]{0.48\textwidth}
    \textbf{Areas of Interest}
    \vspace{0em}
    \begin{itemize}
        \item Mobile Application Development
        \item Full-Stack Development
        \item Web Technologies
    \end{itemize}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.48\textwidth}
    \textbf{Languages}
    \vspace{0em}
    \begin{itemize}
        \item English (B1)
    \end{itemize}
\end{minipage}

\end{document}